Modeling Intervention Strategies for United States TB Control

### 2014-02-15 in_progress/presentations/paper/draft.tex
editted paper comments

{\huge \color{red} Check if first person is better. List of results}

@@

Latently infected individuals may progress to one of two active TB states: Infectious TB (I) or 
Non-Infectious TB (J).  Individuals in both compartments have an increased risk of death from
active TB infection, but only individuals in the Infectious TB compartment are contagious.  
In addition, individuals in all of the infected compartments (F, L, I, J) may be treated or self-cure
themselves of their respective TB health condition.  However, in the model, treatment or self-cure from TB
does not grant immunity, and all healthy individuals are grouped in the Susceptible compartment
and may be re-infected at a later time.

{\huge\color{red} This section is good, but we may want to give a summary of the
differential equations at the end.}

\section{Methods}
\subsection{Basic Structure}
Both the Hill Model (Basic Hill Model) and our extended Model (Extended Hill
Model) were implemented in \texttt{R} as a system of differential equations,
which were solved via the $\texttt{lsoda}$ routine. The systems of differential
equations used to capture basic disease dynamics in the Basic Hill Model are
shown in Figure~\ref{fig:hillEquations}.  In the Extended Hill Model, each flow
rate equation from the Basic Hill Model was separated into its component part
and these were tracked separately. In other words, rather than tracking net flow
into various compartments, the Extended Hill Model tracks flow between all pairs
of compartments separately. Furthermore, these equations were each also supplemented to
also estimate their corresponding US HCS costs.  These equations are detailed in
the\\
{\huge\color{red} Should appendix be capitalized? What about Figure?}\\
appendix,
section~\ref{sec:extendedHillEqs}.  Historical data from 2000-2008 was used to
initialize the model, which was then run up to the year 2100.

>>>>

{\huge \color{red} List of results}

@@

Latently infected individuals may progress to one of two active TB states: Infectious TB (I) or 
Non-Infectious TB (J).  Individuals in both compartments have an increased risk of death from
active TB infection, but only individuals in the Infectious TB compartment are contagious.  
In addition, individuals in all of the infected compartments (F, L, I, J) may be treated or self-cure
themselves of their respective TB health condition.  However, in the model, treatment or self-cure from TB
does not grant immunity, and all healthy individuals are grouped in the Susceptible compartment
and may be re-infected at a later time.\\

\section{Methods}
\subsection{Basic Structure}
Both the Hill Model (Basic Hill Model) and our extended Model (Extended Hill
Model) were implemented in \texttt{R} as a system of differential equations,
which were solved via the $\texttt{lsoda}$ routine. The systems of differential
equations used to capture basic disease dynamics in the Basic Hill Model are
shown in Figure~\ref{fig:hillEquations}.  In the Extended Hill Model, each flow
rate equation from the Basic Hill Model was separated into its component part
and these were tracked separately. In other words, rather than tracking net flow
into various compartments, the Extended Hill Model tracks flow between all pairs
of compartments separately. Furthermore, these equations were each also supplemented to
also estimate their corresponding US HCS costs.  These equations are detailed in
the\\
{\huge\color{red} Add extended Hill equations to the appendix.}\\
appendix,
section~\ref{sec:extendedHillEqs}.  Historical data from 2000-2008 was used to
initialize the model, which was then run up to the year 2100.
